State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-04-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
making a few compressive changes to the spectral section. Got to line 246 before having to stop.

% \begin{equation}
% \mathbf{C} = \left[\begin{array}{{cccc}}
% \int_{\Omega}m(\mathbf{r}_1 - \mathbf{r}')\boldsymbol{\phi}_1(\mathbf{r}')d\mathbf{r}' & \int_{\Omega} m(\mathbf{r}_1 - \mathbf r')\boldsymbol \phi_2(\mathbf r')d\mathbf r' & \dots
% &\int_{\Omega}m(\mathbf r_1 - \mathbf r')\boldsymbol \phi_n(\mathbf
% r')d\mathbf r' \\
% \int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol \phi_1(\mathbf
% r')d\mathbf r'&\int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol
% \phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_2 -
% \mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'\\
% \vdots&\vdots&\ddots&\vdots\\
% \int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol \phi_1(\mathbf
% r')d\mathbf r'&\int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol
% \phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_{n_y} -
% \mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'
% \end{array}\right],
% \end{equation}
% and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
\section{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis was used to identify the number of sensors and basis functions required to accurately represent dynamic spatial fields from sampled observations~\cite{Sanner1992,Scerri2009}. Based on the higher dimension extensions of Shannon's sampling theorem~\cite{Peterson1962}, the spatial bandwidth of the observed field provides a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristic.

The spectral characteristics of the field are governed by the shape of the connectivity kernel or the covariance of the field disturbance. If the bandwidth of the field disturbance covariance was wider than the bandwidth of the connectivity kernel, then the disturbance governs the bandwidth of the system. Conversely, if the bandwidth of the kernel was higher then it will govern the systems bandwidth. Note, the theoretically observable characteristics of the kernel are governed by how it is excited by an input.

Considering the spectral representation of the dynamic field at time $t$ denoted by $V_t(\boldsymbol{\nu})$, multi-dimensional sampling and reconstruction theory dictates that for and accurate representation, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited. Such a condition is usually satisfied due to the band-limiting effect of most practical kernels and the spatially coloured covariance functions \todo{~cite\{some EEG literature here\}}. Thus the spectral response $V_t(\boldsymbol{\nu})$ is usually band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency. Note that for the 3-dimensional, homogeneous and isotopic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$. Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors, $\Delta_s$, needs to satisfy 
\begin{equation}
	\label{eq:MinimumSensorDistance} \Delta_s < \frac{1}{2\rho\nu_c}, 
\end{equation}
where $\rho \in \mathbb{R} \ge 1$ is an oversampling parameter. Satisfying this condition is required for the hidden dynamic field $v_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}(t)$. If the condition is not satisfied, spatial aliasing will occur.

>>>>

% \begin{equation}
% \mathbf{C} = \left[\begin{array}{{cccc}}
% \int_{\Omega}m(\mathbf{r}_1 - \mathbf{r}')\boldsymbol{\phi}_1(\mathbf{r}')d\mathbf{r}' & \int_{\Omega} m(\mathbf{r}_1 - \mathbf r')\boldsymbol \phi_2(\mathbf r')d\mathbf r' & \dots
% &\int_{\Omega}m(\mathbf r_1 - \mathbf r')\boldsymbol \phi_n(\mathbf
% r')d\mathbf r' \\
% \int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol \phi_1(\mathbf
% r')d\mathbf r'&\int_{\Omega}m(\mathbf r_2 - \mathbf r')\boldsymbol
% \phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_2 -
% \mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'\\
% \vdots&\vdots&\ddots&\vdots\\
% \int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol \phi_1(\mathbf
% r')d\mathbf r'&\int_{\Omega}m(\mathbf r_{n_y} - \mathbf r')\boldsymbol
% \phi_2(\mathbf r')d\mathbf r'& \dots &\int_{\Omega}m(\mathbf r_{n_y} -
% \mathbf r')\boldsymbol \phi_n(\mathbf r')d\mathbf r'
% \end{array}\right],
% \end{equation}
% and $m(\mathbf r_n - \mathbf{r}')$ is the observation kernel.
\section{Spectral Analysis and Model Selection}
\label{SpectralAnalysisSection}

Spectral analysis was used to identify both the number of sensors and the number of basis functions required to reconstruct the membrane voltage from sampled observations \cite{Sanner1992,Scerri2009}. Based on a two dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristic.

The spectral characteristics of the field are governed by the shape of the connectivity kernel and the covariance of the field disturbance. If the bandwidth of the field disturbance covariance is wider than the bandwidth of the connectivity kernel, then the disturbance covariance governs the bandwidth of the system. Conversely, a wider kernel bandwidth will govern the system bandwidth. \wtf{this bit incites trouble: Note, the theoretically observable characteristics of the kernel are governed by how it is excited by an input.}

Let the spectral representation of the dynamic field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$. Then, for an accurate representation, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited. Such a condition is usually satisfied due to the band-limiting effect of most practical kernels and covariance functions \todo{~cite\{some EEG literature here\}}. Thus we can assume that the spectral response $V_t(\boldsymbol{\nu})$ is band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency. Note that for the 3-dimensional, homogeneous and isotropic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c ~ \nu_c]^\top$. Given such a band-limited field and based on Shannon's sampling theorem, the distance between adjacent sensors, $\Delta_s$, needs to satisfy 
\begin{equation}
	\label{eq:MinimumSensorDistance} \Delta_s < \frac{1}{2\rho\nu_c}, 
\end{equation}
where $\rho \in \mathbb{R} \ge 1$ is an oversampling parameter. Satisfying this condition is required for the hidden dynamic field $v_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}(t)$. If the condition is not satisfied, spatial aliasing will occur.
